Algorithms for the Automated Correction of Vertical Drift in Eye Tracking Data

### 2020-07-25 manuscript/manuscript.tex
Typos

\noindent where $l_y$ is the vertical center point of the intended line---the \textit{y}~value that the reader is targeting. This models three types of distortion: noise, slope, and shift. Additionally, we simulate two types of regression that are characteristic of normal reading behavior and can disrupt algorithmic correction. Together, these five phenomena are illustrated in Fig.~\ref{fig04} and described below.

@@

Particularly interesting is a comparison between the winners in their category. Contrary to \texttt{warp}, \texttt{cluster} is entirely invariant to between-line regressions. However, \texttt{warp} is much better than \texttt{cluster} at managing general noise and slope. This might seem like bad news for the community, because there is no all-around best solution. At the same time though, this also means that researchers will always have a good option available depending on what kind of data they have. For example, if the line spacing is quite tight, the eye tracking data is more likely be negatively impacted by distortion, making a sequential algorithm a better choice; conversely, if lines are spread far apart, a relative-positional algorithm might work better.

>>>>

\noindent where $l_y$ is the vertical center point of the intended line---the \textit{y}~value that the reader is targeting. This models three types of distortion: noise, slope, and shift. Additionally, we simulate two types of regression that are characteristic of normal reading behavior but which can nevertheless disrupt algorithmic correction. Together, these five phenomena are illustrated in Fig.~\ref{fig04} and described below.

@@

Particularly interesting is a comparison between the winners in their category. Contrary to \texttt{warp}, \texttt{cluster} is entirely invariant to between-line regressions. However, \texttt{warp} is much better than \texttt{cluster} at managing general noise and slope. This might seem like bad news for the community, because there is no all-around best solution. At the same time though, this also means that researchers will always have a good option available depending on what kind of data they have. For example, if the line spacing is quite tight, the eye tracking data is more likely to be negatively impacted by distortion, making a sequential algorithm a better choice; conversely, if lines are spread far apart, a relative-positional algorithm might work better.
